Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-04-05 paper/paper-nature_format.qmd
small edits

The next step was to further develop our script to produce tidy data sets, as defined and introduced by @Wickham2014. These contain all parsed text elements, where each statement is separated onto its own row with details about the speaker, and rows are maintained in chronological order. This first involved correcting the variable classes and adding several indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or `<sub-debate.1> versus `<sub-debate.2>`. The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed. In other words, any interjections, comments made by The Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string. As such, the name, name ID, electorate and party details were only provided for the person whose turn it was to speak. Further details on the intricacies of the task of splitting these speeches in a way that would be generalizable across sitting days are provided in @sec-interject.

@@

We then created lists using both the `interject` and `main` dataframes to capture all the names of individuals who spoke that day. We added the names of all members in a number of unique formats, due to the frequent variation in how names are transcribed in Hansard. When a member interjects or continues a speech, the usual form of their name is a title followed by their first name or first initial and/or last name. There is also variation in the capitalization of these names.[^2] Another source of variation is in individuals with more than one first name, as sometimes only their initial first name is written, while other times their entire first name is written. Additionally, some surnames have punctuation, and some surnames have specific capitalization such as "McCormack", where even in full capitalization, the first "c" remains lower case. This variation demands careful consideration when writing regular expression patterns. In these lists we also accounted for any general interjection statements that were not attributed to an individual, such as "An opposition member interjecting-".

[^2]: Sometimes when someone's first name is included, only their last name is capitalized, while sometimes their full name is capitalized, or other times neither are capitalized.

@@

Having developed a successful methodology for splitting interjections, we used this to inform our general approach in the third and fourth scripts. However, the difference in data cleaning used in these scripts necessitated some departure from the original methodology. As discussed in @sec-diff, we used string patterns extracted from `<talk.start>` nodes to separate speeches. As evident in @fig-xml3, `<talk.start>` nodes are nested within `<interjection>` nodes, meaning that the patterns of data from interjection statements were separated out in the process. In other words, our approach to data cleaning in the third and fourth scripts separated out interjections in the process. This meant that we did not need to create lists of names and titles for which to search in the text as we did before. However, we used the same list of general interjection statements on which to separate as was used in the first two scripts. We then did an additional check for statements that may have not been separated due to how they were embedded in the XML, and separated those out where needed.[^3]

[^3]: While most statements were categorized in their own child-node and hence captured through pattern-based separation, some were not individually categorized, and had to be split manually in this step.

@@

Our database is available in both CSV and parquet formats. It covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022. So there are 1,517 files for each format. All data records are available on the general-purpose repository Zenodo, at https://doi.org/10.5281/zenodo.7336075 [@katz_2023]. For each file, each row contains an individual statement, with details on the individual speaking. For general statements transcribed as made by "Honourable members" for example, these variables cannot be specified. @tbl-vars provides an overview of each variable found in the database.

@@

We developed a script to perform automated tests on each file in our database, to enhance its quality and consistency. Our first test validates that the date specified in each file name matches the date specified in its corresponding XML session header.[^4] Every file passed this test, and we detected one discrepancy in an XML file from 03 June 2009, where its session header contained the wrong date. We validated that our file name and date was correct by checking the official PDF release from that sitting day.

[^4]: As seen in @fig-xml1, the first child node of the `<session.header>` element is the date.

>>>>

The next step was to further develop our script to produce tidy data sets, as defined and introduced by @Wickham2014. These contain all parsed text elements, where each statement is separated onto its own row with details about the speaker, and rows are maintained in chronological order. This first involved correcting the variable classes and adding several indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or `<sub-debate.1> versus`\<sub-debate.2\>\`. The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed. In other words, any interjections, comments made by The Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string. As such, the name, name ID, electorate and party details were only provided for the person whose turn it was to speak. There were many intricacies in the task of splitting these speeches in a way that would be generalizable across sitting days. Details on these are provided in @sec-interject.

@@

We then created lists using both the `interject` and `main` dataframes to capture all the names of individuals who spoke that day. We added the names of all members in a number of unique formats, due to the frequent variation in how names are transcribed in Hansard. When a member interjects or continues a speech, the usual form of their name is a title followed by their first name or first initial and/or last name. There is also variation in the capitalization of these names.[^1] Another source of variation is in individuals with more than one first name, as sometimes only their initial first name is written, while other times their entire first name is written. Additionally, some surnames have punctuation, and some surnames have specific capitalization such as "McCormack", where even in full capitalization, the first "c" remains lower case. This variation demands careful consideration when writing regular expression patterns. In these lists we also accounted for any general interjection statements that were not attributed to an individual, such as "An opposition member interjecting-".

[^1]: Sometimes when someone's first name is included, only their last name is capitalized, while sometimes their full name is capitalized, or other times neither are capitalized.

@@

Having developed a successful methodology for splitting interjections, we used this to inform our general approach in the third and fourth scripts. However, the difference in data cleaning used in these scripts necessitated some departure from the original methodology. As discussed in @sec-diff, we used string patterns extracted from `<talk.start>` nodes to separate speeches. As evident in @fig-xml3, `<talk.start>` nodes are nested within `<interjection>` nodes, meaning that the patterns of data from interjection statements were separated out in the process. In other words, our approach to data cleaning in the third and fourth scripts separated out interjections in the process. This meant that we did not need to create lists of names and titles for which to search in the text as we did before. However, we used the same list of general interjection statements on which to separate as was used in the first two scripts. We then did an additional check for statements that may have not been separated due to how they were embedded in the XML, and separated those out where needed.[^2]

[^2]: While most statements were categorized in their own child-node and hence captured through pattern-based separation, some were not individually categorized, and had to be split manually in this step.

@@

Our database is available in both CSV and parquet formats. It covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022, so there are 1,517 files for each format. All data records are available on the general-purpose repository Zenodo, at https://doi.org/10.5281/zenodo.7336075 [@katz_2023]. For each file, each row contains an individual statement, with details on the individual speaking. For general statements transcribed as made by "Honourable members" for example, these variables cannot be specified. @tbl-vars provides an overview of each variable found in the database.

@@

We developed a script to perform automated tests on each file in our database, to enhance its quality and consistency. Our first test validates that the date specified in each file name matches the date specified in its corresponding XML session header.[^3] Every file passed this test, and we detected one discrepancy in an XML file from 03 June 2009, where its session header contained the wrong date. We validated that our file name and date was correct by checking the official PDF release from that sitting day.

[^3]: As seen in @fig-xml1, the first child node of the `<session.header>` element is the date.
